
---
author: |
  | William Findlay
title: |
  | Honours Thesis Pre-Proposal
subtitle: |
  | Implementing Process Homeostasis Using
  | Extended Berkeley Packet Filtering
date: \today
bibliography: /home/housedhorse/.bibs/uni.bib
csl: /home/housedhorse/.bibs/ieee.csl
subparagraph: yes
header-includes: |
  ```{=latex}
  \usepackage{float}
  \usepackage{listings}
  \usepackage[hang,bf]{caption}
  \usepackage{framed}
  \usepackage[section]{placeins}

  \usepackage[dvipsnames,table]{xcolor}

  \usepackage{pifont}

  \allowdisplaybreaks

  \usepackage[bottom]{footmisc}
  % fancy headers/footers
  \makeatletter
  \usepackage{fancyhdr}
  \lhead{\@author}
  \chead{}
  \rhead{\@title}
  \lfoot{}
  \cfoot{\thepage}
  \rfoot{}
  \renewcommand{\headrulewidth}{0.4pt}
  \makeatother

  \usepackage{amsmath, amsfonts,amssymb, amsthm}
  \usepackage{siunitx}
  \usepackage[boxruled,lined,linesnumbered,titlenumbered]{algorithm2e}

  \usepackage{setspace}
  \usepackage{changepage}
  \usepackage[explicit]{titlesec}
  \usepackage{aliascnt}

  \floatplacement{figure}{!htbp}
  \floatplacement{table}{!htbp}
  \lstset{numbers=left,breaklines=true,frame=single,language=Python,captionpos=t,abovecaptionskip={\abovecaptionskip},
  belowcaptionskip={0.5em},aboveskip=\intextsep,showstringspaces=false,identifierstyle=\color{Blue},
  commentstyle={\color{OliveGreen}},keywordstyle={\bfseries\color{Orange}},stringstyle=\color{Purple},mathescape=true}
  \setlength{\captionmargin}{1in}

  \newgeometry{margin=1in}

  \newtheoremstyle{plain}
  {12pt}   % ABOVESPACE
  {12pt}   % BELOWSPACE
  {\itshape}  % BODYFONT
  {0pt}       % INDENT (empty value is the same as 0pt)
  {\bfseries} % HEADFONT
  {.}         % HEADPUNCT
  {5pt plus 1pt minus 1pt} % HEADSPACE
  {}          % CUSTOM-HEAD-SPEC

  \newtheoremstyle{definition}
  {12pt}   % ABOVESPACE
  {12pt}   % BELOWSPACE
  {\normalfont}  % BODYFONT
  {0pt}       % INDENT (empty value is the same as 0pt)
  {\bfseries} % HEADFONT
  {.}         % HEADPUNCT
  {5pt plus 1pt minus 1pt} % HEADSPACE
  {}          % CUSTOM-HEAD-SPEC

  \newtheoremstyle{remark}
  {12pt}   % ABOVESPACE
  {12pt}   % BELOWSPACE
  {\normalfont}  % BODYFONT
  {0pt}       % INDENT (empty value is the same as 0pt)
  {\itshape} % HEADFONT
  {.}         % HEADPUNCT
  {5pt plus 1pt minus 1pt} % HEADSPACE
  {}          % CUSTOM-HEAD-SPEC

  \theoremstyle{plain}

  % define theorem
  \newtheorem{theorem}{Theorem}[section]
  \providecommand*{\theoremautorefname}{Theorem}

  % define lemma
  \newtheorem{lemma}{Lemma}[section]
  \providecommand*{\lemmaautorefname}{Lemma}

  % define claim
  \newtheorem{claim}{Claim}[section]
  \providecommand*{\claimautorefname}{Claim}

  % define corollary
  \newtheorem{corollary}{Corollary}[section]
  \providecommand*{\corollaryautorefname}{Corollary}

  % define proposition
  \newtheorem{proposition}{Proposition}[section]
  \providecommand*{\propositionautorefname}{Proposition}

  % define conjecture
  \newtheorem{conjecture}{Conjecture}[section]
  \providecommand*{\conjectureautorefname}{Conjecture}

  \theoremstyle{remark}

  % define observation
  \newtheorem{observation}{Observation}[section]
  \providecommand*{\observationautorefname}{Observation}

  % define remark
  \newtheorem{remark}{Remark}[section]
  \providecommand*{\remarkautorefname}{Remark}

  \theoremstyle{definition}

  % define example
  \newtheorem{example}{Example}[section]
  \providecommand*{\exampleautorefname}{Example}

  % define definition
  \newtheorem{definition}{Definition}[section]
  \providecommand*{\definitionautorefname}{Definition}

  \newcommand{\blackbox}{\hfill$\blacksquare$}
  \usepackage{tikz}
  \newcommand*\circled[1]{\tikz[baseline=(char.base)]{
              \node[shape=circle,draw,inner sep=2pt] (char) {#1};}}

  \renewcommand{\labelitemi}{$\bullet$}
  \renewcommand{\labelitemii}{\ding{226}}
  \renewcommand{\labelitemiii}{\small$\blacksquare$}
  \renewcommand{\labelitemiv}{\small$\triangleright$}

  \titleformat{\paragraph} % command to change
  [runin]                  % shape  (runin, etc.)
  {\bfseries}              % format (bfseries, itshape, etc.)
  {}                       % label  (thesection, thesubsection, etc.)
  {0em}                    % separation between label and body
  {#1}        % before the body
  [.]                       % after the body

  \titleformat{\subparagraph} % command to change
  [runin]                  % shape  (runin, etc.)
  {\itshape}              % format (bfseries, itshape, etc.)
  {}                       % label  (thesection, thesubsection, etc.)
  {0em}                    % separation between label and body
  {#1}        % before the body
  [.]                       % after the body

  \let\lil\lstinputlisting
  \usepackage{afterpage}
  \hypersetup{colorlinks, allcolors=., urlcolor=blue}

  \usepackage{etoolbox}% http://ctan.org/pkg/etoolbox
  \makeatletter
  \patchcmd{\lst@GLI@}% <command>
    {\def\lst@firstline{#1\relax}}% <search>
    {\def\lst@firstline{#1\relax}\def\lst@firstnumber{#1\relax}}% <replace>
    {\typeout{listings firstnumber=firstline}}% <success>
    {\typeout{listings firstnumber not set}}% <failure>
  \makeatother

  \renewcommand\lstlistlistingname{List of Listings}
  \usepackage{chngcntr}
  \counterwithin{figure}{section}
  \counterwithin{table}{section}

  \usepackage{booktabs}
  \usepackage{longtable}
  \usepackage{array}
  \usepackage{multirow}
  \usepackage{wrapfig}
  \usepackage{float}
  \usepackage{colortbl}
  \usepackage{pdflscape}
  \usepackage{tabu}
  \usepackage{threeparttable}
  \usepackage{threeparttablex}
  \usepackage[normalem]{ulem}
  \usepackage{makecell}

  \renewcommand{\sectionautorefname}{Section}
  \renewcommand{\subsectionautorefname}{Subection}
  \renewcommand{\subsubsectionautorefname}{Subection}
  \renewcommand{\paragraphautorefname}{}
  \renewcommand{\subparagraphautorefname}{}

  \usepackage{nameref}

  \makeatletter
  \renewcommand{\theparagraph}{\bfseries \@currentlabelname}
  \renewcommand{\thesubparagraph}{\itshape \@currentlabelname}
  \makeatother

  \usepackage{enumitem}
  \setitemize{itemsep=0em}

  \usepackage[final]{pdfpages}
  \usepackage{lipsum}

  \let\oldmaketitle\maketitle
  \renewcommand{\maketitle}{\relax}
  ```
output:
  pdf_document:
    number_sections: true
    fig_crop: true
    fig_caption: true
    keep_tex: false
---
```{r,include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(kableExtra.latex.load_packages = FALSE)
library(kableExtra)
library(lubridate)
```
\pagestyle{fancy}
\thispagestyle{plain}
\counterwithin{lstlisting}{section}
\includepdf{cover-page-filled.pdf}
\renewcommand{\maketitle}{\oldmaketitle}
\setcounter{page}{1}
\maketitle

# Overview of Thesis

This section presents an overview of the thesis including motivation, objectives, equipment requirements,
and expected deliverables.

## Motivation

## Main Objectives

## Equipment Requirements

## Expected Deliverables

# Bi-Weekly Schedule for First Term (Fall 2019)

\autoref{fall-sched} presents a bi-weekly schedule for the fall 2019 term. This term will be used
primarily for background research on Process Homeostasis and Extended Berkeley Packet Filtering in
the Linux Kernel.

<!-- print table for bi-weekly fall schedule -->

```{r}
# weekly
dates = c(seq(as.Date("2019-09-04"), as.Date("2019-12-06"), by = 'week'))

# biweekly
start_dates = dates[seq(1,length(dates),2)]
end_dates = start_dates + 13
end_dates[7] = as.Date("2019-12-06")

dates = paste(format(start_dates, "%b %d"), "-", format(end_dates, "%b %d, %Y"))
tasks = NULL

for(i in 1 : length(dates)) {
  tasks = c(tasks,NA)
}

tasks[1] = "Background research on eBPF"
tasks[2] = "Background research on pH"
tasks[3] = "Explore other intrusion detection methods"
tasks[4] = "Explore other eBPF implementations of intrusion detection"
tasks[5] = "Determine best approach to solve the problem"
tasks[6] = "Draft thesis proposal report"
tasks[7] = "Finalize thesis proposal report"

dates[7] = paste(dates[7],footnote_marker_alphabet(1))

df = data.frame(week=dates,task=tasks)

names(df) = c("Bi-weekly Period","Task")

df %>%
  kable(longtable=F, align = c('r','l'), caption=('\\label{fall-sched}A bi-weekly schedule for the fall 2019 term.'), escape=F) %>%
  kable_styling(latex_options=c('striped','hold_position')) %>%
  row_spec(0,bold=T) %>%
  column_spec(2,width='30em') %>%
  add_footnote("This period is slightly shorter to reflect the end of the term.")
```
